%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{990000}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Himal}{Shrestha}

\position{PhD, Bioinformatics}
\address{La Trobe University}

\email{\href{mailto:stha.himal2007@gmail.com}{\nolinkurl{stha.himal2007@gmail.com}}}
%\homepage{himal2007.netlify.app}
\orcid{0000-0002-4470-4830}
\github{himal2007}
\linkedin{himal-shrestha}
\twitter{@himal2007}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{As a PhD graduate in Bioinformatics with expertise in computational and mathematical modelling, I am passionate about using data to predict, prevent, and eliminate diseases. My research at La Trobe University involved studying the transmission of parasitic disease, called river blindness, by integrating genomic, environmental, and epidemiological data with a variety of modelling and analytical approaches. I am now seeking new opportunities that will enable me to utilise and expand my current skill sets.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May 2023}
    {Himal Shrestha~~~·~~~CV}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{La Trobe University}{PhD in Bioinformatics}{Melbourne, Australia}{2019-2023(submitted)}{\begin{cvitems}
\item \textbf{Thesis}: Geospatial modelling of onchocerciasis transmission.
\end{cvitems}}
    \cventry{La Trobe University}{Master of Biotechnology and Bioinformatics}{Melbourne, Australia}{2017-2019}{}\vspace{-4.0mm}    
    \cventry{Kathmandu University}{Bachelor of Science in Human Biology}{Dhulikhel, Nepal}{2012-2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\begin{cventries}
    \cventry{\textbf{Computational skills}}{}{}{}{\begin{cvitems}
\item Programming languages: R, Python, MATLAB, Linux Shell, Bash, Julia, javascript and C
\item GIS softwares: Earth Engine, QGIS
\item Markup and version control: LaTex, Markdown, YAML, Git, GitHub, Bitbucket, VSCode
\item Bioinformatics databases: NCBI, UniProt, EMBL-EBI, DDBJ, Wormbase and Vectorbase
\item Miscellaneous: High Performance Computing Clusters, Cloud computing with AWS and Oracle-Cloud, RShiny, SPSS, Origin, Microsoft packages
\end{cvitems}}
    \cventry{\textbf{Wet Lab skills}}{}{}{}{\begin{cvitems}
\item Samples: Clinical (blood, sputum, urine), microbiological (bacteria, fungus) and molecular samples (protein, RNA, plasmid and DNA)
\item Molecular techniques: DNA and plasmid extraction, Gel Electrophoresis, SDS PAGE, ELISA, Cloning with restriction endonuclease, Primer Design for PCR, Protein separation with IMAC
\end{cvitems}}
    \cventry{\textbf{Organizational skills}}{}{}{}{\begin{cvitems}
\item Initiated a contract research organisation called, \textcolor{awesome}{\href{https://ankaanalytica.com/}{Anka Analytica}} with a group of post-docs in Australia
\item Active committee member: PAM-HDR (2020), COMBINE-AU (2020-2022)
\end{cvitems}}
    \cventry{\textbf{Communication skills}}{}{}{}{\begin{cvitems}
\item Verbal: presentations in seminar, conferences, teaching and co-host of a podcast, \textcolor{awesome-emerald}{\href{https://anchor.fm/sciencekakura}{Science ka Kura}}
\item Written: journal articles, thesis, newsletters at student societies (PAM-HDR, COMBINE) and report writing
\end{cvitems}}
\end{cventries}

\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{La Trobe University}{Post-doctoral researcher (Bioinformatics/infectious disease modelling)}{Melbourne, Australia}{Apr, 2023-Ongoing}{\begin{cvitems}
\item Formulating empirical and/or mechanistic transmission models utilising genomic, environmental and epidemiological data and supervise students working on related research.
\end{cvitems}}
    \cventry{La Trobe University}{Casual academic}{Melbourne, Australia}{Feb, 2020-Oct, 2022}{\begin{cvitems}
\item BIO5INF (Bioinformatics), BIO1MGC (Molecules, Genes and Cells),  and BIO1EEB (Ecology, Evolution and Biodiversity)
\item La Trobe Outreach Demonstrator: Bytesize Bioinformatics
\end{cvitems}}
    \cventry{La Trobe University}{Research assistant}{Melbourne, Australia}{Jul-Aug, 2019}{\begin{cvitems}
\item Performed analysis of embryogram and skin snip data of female \textit{Onchocerca volvulus} parasite
\end{cvitems}}
    \cventry{Purbanchal University}{Lecturer}{Bhaktapur, Nepal}{Jan-Jun, 2017}{\begin{cvitems}
\item Anatomy and Physiology, Pharmacology and Toxicology
\end{cvitems}}
\end{cventries}

\hypertarget{awards}{%
\section{Awards}\label{awards}}

\begin{cventries}
    \cventry{Asia Pacific Consortium of Mathematics for Industry}{Best poster prize}{Melbourne, Australia}{2022}{}\vspace{-4.0mm}
    \cventry{American Society of Tropical Medicine \& Hygiene}{ASTMH Young Investigator Award (First-tier Mention)}{Seattle, Washington, United States}{2022}{}\vspace{-4.0mm}
    \cventry{Genetics Society of Australasia}{The Jenny Graves Prize for best student short presentation}{ComBio22, Melbourne, Australia}{2022}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{LTU Postgraduate Research Scholarship (LTUPRS) Award}{Melbourne, Australia}{2019-2023}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{Pro Vice Chancellor's Commendation 2018}{Melbourne, Australia}{2019}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{research-grants}{%
\section{Research grants}\label{research-grants}}

\begin{cventries}
    \cventry{UNICEF/UNDP/World Bank/WHO Special Programme for Research and Training in Tropical Diseases (TDR/WHO) (US\$108,000)}{Co-investigator/Sub-awardee}{}{2021-2022}{\begin{cvitems}
\item  \textbf{Project}: Population genetic tools for onchocerciasis control programmes to determine transmission zones.
\end{cvitems}}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{cventries}
    \cventry{\textbf{Journal publications}}{}{}{}{\begin{cvitems}
\item \textbf{Shrestha H}, McCulloch K, Hedtke SM, Grant WN. Geospatial modeling of pre-intervention nodule prevalence of \textit{Onchocerca volvulus} in Ethiopia as an aid to onchocerciasis elimination. Cotton J, editor. PLoS Negl Trop Dis. 2022 Jul 18;16(7):e0010620.
\item Gyawali P, Tamrakar D, Shrestha A, \textbf{Shrestha H}, Karmacharya S, Bhattarai S, et al. Consumer acceptance and preference for brown rice-A mixed-method qualitative study from Nepal. Food Sci Nutr. 2022 Mar 4;fsn3.2803.
\item Gyawali P, \textbf{Shrestha H}, Pant V, Risal P, Gautam S. C-reactive Protein to Albumin Ratio among Patients Admitted to Intensive Care Unit of a Tertiary Care Hospital: A Descriptive Crosssectional Study. J Nepal Med Assoc. 2021 Dec 11;59(244):1247-51.
\item R Shrestha, DP Subedi, S Adhikari, A Maharjan, \textbf{H Shrestha}, GR Pandey (2017). Experimental Study of Atmospheric Pressure Argon Plasma Jet-Induced Strand Breakage in Large DNA Molecules, Plasma Medicine, vol. 7, no. 1. doi:10.1615/PlasmaMed.2017019986
\item JTM Shrestha, \textbf{H Shrestha}, M Prajapati, A Karkee, A Maharjan (2017). Adverse Effcts of Oral Hypoglycemic Agents and Adherence to them among Patients with Type 2 Diabetes Mellitus in Nepal, Journal of Lumbini Medical College, vol. 5, no. 1, pp. 34-40. doi:10.22502/jlmc.v5i1.126
\end{cvitems}}
    \cventry{\textbf{Preprint}}{}{}{}{\begin{cvitems}
\item \textbf{Shrestha H}, McCulloch K, Chisholm RH, Armoo S, Vierigh F, Sirwani N, et al. Synthesising environmental, epidemiological, and genetic data to assist decision making for onchocerciasis elimination. Epidemiology; 2023 Feb. doi:10.1101/2023.02.14.23285937
\end{cvitems}}
    \cventry{\textbf{Conference presentations and posters}}{}{}{}{\begin{cvitems}
\item \textbf{H Shrestha}, K McCulloch, SM Hedtke, WN Grant (2021). Geospatial modeling of the baseline \textit{Onchocerca volvulus} nodule prevalence in Ethiopia as an aid to elimination. Poster presentation at ASTMH 2022 Annual Meeting,  Seattle Convention Center, United States, 30 Oct - 3 Nov, 2022.
\item \textbf{H Shrestha}, SM Hedtke, RH Chisholm, WN Grant (2021). Landscape genetics and persistence of Onchocerciasis transmission in Ghana. Lightning talk at ComBio22, Melbourne Convention and Exhibition Centre (MCEC),27-30 Sep, 2022.
\item \textbf{H Shrestha}, K McCulloch, SM Hedtke, WN Grant (2021). Geospatial mapping of onchocerciasis prevalence in Ethiopia. Spatial and Temporal Statistics Symposium (STSS), University of Wollongong (Virtual), February 17-19, 2021.
\item \textbf{H Shrestha} (2019). Elucidating ivermectin's action on reproduction of adult female \textit{Onchocerca volvulus} from embryogram data: the basis for the embryostatic phenotype. PRISM2 Annual Conference, Woodward Conference Centre, Carlton, Victoria, November 12-13, 2019.
\item \textbf{H Shrestha}, SM Hedtke, K McCulloch, S Wanji, WN Grant (2019). Effect of ivermectin treatment on adult female \textit{Onchocerca volvulus} from embryogram data: evidence for periodicity of reproduction and the basis for the embryostatic phenotype. Oral presentation (15 mins) at annual meeting of Australian Society for Parasitology, Adelaide Convention Centre, South Australia, July 8-11, 2019.
\item \textbf{H Shrestha}, A Maharjan, S Shrestha (2016). Attitudes Towards Menstruation of Pre-menstruating Adolescent School Girls. Poster presentation at 7th National Conference on Science and Technology, Kathmandu, Nepal, March 29-21, 2016.
\end{cvitems}}
\end{cventries}

\hypertarget{References}{%
\section{References}\label{References}}

\newcommand*{\emaillink}[1]{{\fontsize{8pt}{1em}\bodyfont\scshape\color{awesome} #1}}

\newcommand{\cvdoublecolumn}[2]{%
	\begin{minipage}[t]{{.45\linewidth}}#1\end{minipage}%
	\hfill%
	\begin{minipage}[t]{{.45\linewidth}}#2\end{minipage}%
}

\newcommand{\cvreference}[5]{
	\entrytitlestyle{#1}\newline
	\descriptionstyle{#2}\newline
	\descriptionstyle{#3}\newline
	\faHome\acvHeaderIconSep~\descriptionstyle{#4}\newline
	\href{mailto:#5}{\faEnvelope\acvHeaderIconSep~\emaillink{#5}\newline}}

\cvdoublecolumn{\cvreference{Prof Warwick Grant}
	{Head of Discipline, Genetics}
	{Department of Environment and Genetics, La Trobe University}
	{Bundoora, Victoria, Australia}
	{W.Grant@latrobe.edu.au}
}
{\cvreference{Dr Shannon Hedtke}
	{Research Fellow}
	{Department of Environment and Genetics, La Trobe University}
	{Bundoora, Victoria, Australia}
	{S.Hedtke@latrobe.edu.au}
}

\end{document}
