%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{990000}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Himal}{Shrestha}

\position{PhD Student}
\address{La Trobe University}

\email{\href{mailto:H.Shrestha@latrobe.edu.au}{\nolinkurl{H.Shrestha@latrobe.edu.au}}}
\homepage{himal2007.netlify.app}
\orcid{0000-0002-4470-4830}
\github{himal2007}
\linkedin{himal-shrestha}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{As a PhD graduate in Bioinformatics with expertise in
computational and mathematical modelling, I am passionate about using
data to predict, prevent, and eliminate diseases. My research at La
Trobe University involved studying the transmission of parasitic
disease, called river blindness, by integrating genomic, environmental, and
epidemiological data with a variety of modelling and analytical
approaches. I am now seeking new opportunities that will enable me to
utilise and expand my current skill sets.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May 2023}
    {Himal Shrestha~~~·~~~CV}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{La Trobe University}{PhD in Bioinformatics}{Melbourne, Australia}{2019-2023(submitted)}{\begin{cvitems}
\item Project: Geospatial modelling of onchocerciasis transmission.
\end{cvitems}}
    \cventry{La Trobe University}{Master of Biotechnology and Bioinformatics}{Melbourne, Australia}{2017-2019}{\begin{cvitems}
\item Thesis: Analysis of ivermectin action on adult female \textit{Onchocerca volvulus} from embryogram data: evidence for reproductive periodicity and the basis for the embryostatic phenotype.
\end{cvitems}}
    \cventry{Kathmandu University}{Bachelor of Science in Human Biology}{Dhulikhel, Nepal}{2012-2016}{\begin{cvitems}
\item Thesis: Assessment of C-Reactive Protein/Albumin ratio for predicting outcome in critically ill patients with various underlying diseases.
\end{cvitems}}
\end{cventries}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\begin{cventries}
    \cventry{\textbf{Computational skills}}{}{}{}{\begin{cvitems}
\item Programming languages: R, Python, MATLAB, Bash, Julia, javascript and C
\item GIS softwares: Earth Engine, QGIS
\item Markup and version control: LaTex, Markdown, RMarkdown, CSV, JSON, YAML, Git, VSCode
\item Bioinformatics databases: NCBI, UniProt, EMBL-EBI, DDBJ, Wormbase and Vectorbase
\item Miscellaneous: High Performance Computing Clusters, Cloud computing with AWS and Oracle-Cloud, RShiny, SPSS, Origin, Microsoft packages
\end{cvitems}}
    \cventry{\textbf{Wet Lab skills}}{}{}{}{\begin{cvitems}
\item Samples: Clinical (blood, sputum, urine), microbiological (bacteria, fungus) and molecular samples (protein, RNA, plasmid and DNA)
\item Molecular techniques: DNA and plasmid extraction, Gel Electrophoresis, SDS PAGE, ELISA, Cloning with restriction endonuclease, Primer Design for PCR, Protein separation with IMAC
\item Instruments: Spectrophotometer, Centrifuge, PCR thermal cycler, water bath, incubators and autoclaves
\end{cvitems}}
    \cventry{\textbf{Organizational skills}}{}{}{}{\begin{cvitems}
\item Initiated a contract research organisation called, Anka Analytica with a group of post-docs in Australia
\item Active committee member: PAM-HDR (2020), COMBINE-AU (2020-2022)
\item Initiated undergraduate student club, One Class One Community (OCOC) with approximately 200 members
\item Experience of working as a team with diverse group of people
\end{cvitems}}
    \cventry{\textbf{Communication skills}}{}{}{}{\begin{cvitems}
\item Verbal: presentations in seminar, conferences, teaching and co-host of a podcast, \href{https://anchor.fm/sciencekakura}{Science ka Kura}
\item Written: journal articles, thesis, newsletters at student societies (PAM-HDR, COMBINE) and report writing
\end{cvitems}}
\end{cventries}

\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{La Trobe University}{Post-doctoral researcher (Bioinformatics/infectious disease modelling)}{Melbourne, Australia}{Apr, 2023-Ongoing}{\begin{cvitems}
\item Formulating empirical and/or mechanistic transmission models utilising genomic, environmental and epidemiological data and supervise students working on related research.
\end{cvitems}}
    \cventry{La Trobe University}{Casual academic}{Melbourne, Australia}{Feb, 2020-Oct, 2022}{\begin{cvitems}
\item BIO5INF (Bioinformatics)
\item BIO1MGC (Molecules, Genes and Cells)
\item BIO1EEB (Ecology, Evolution and Biodiversity)
\end{cvitems}}
    \cventry{La Trobe University}{La Trobe Outreach Demonstrator}{Melbourne, Australia}{Jan, 2020}{\begin{cvitems}
\item Bytesize Bioinformatics
\end{cvitems}}
    \cventry{La Trobe University}{Research assistant}{Melbourne, Australia}{Jul-Aug, 2019}{\begin{cvitems}
\item Performed analysis of embryogram and skin snip data of female \textit{Onchocerca volvulus} parasite
\item Assisted in analysis of genomic data generated in the lab
\end{cvitems}}
    \cventry{Purbanchal University}{Lecturer}{Bhaktapur, Nepal}{Jan-Jun, 2017}{\begin{cvitems}
\item Anatomy and Physiology
\item Pharmacology and Toxicology
\end{cvitems}}
\end{cventries}

\hypertarget{awards}{%
\section{Awards}\label{awards}}

\begin{cventries}
    \cventry{Asia Pacific Consortium of Mathematics for Industry}{Best poster prize}{Melbourne, Australia}{2022}{}\vspace{-4.0mm}
    \cventry{American Society of Tropical Medicine \& Hygiene}{ASTMH Young Investigator Award (First-tier Mention)}{Seattle, Washington, United States}{2022}{}\vspace{-4.0mm}
    \cventry{American Society of Tropical Medicine \& Hygiene}{ASTMH annual meeting travel award}{Seattle, Washington, United States}{2022}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{SABE HDR student research support award}{Melbourne, Australia}{2022}{}\vspace{-4.0mm}
    \cventry{Genetics Society of Australasia}{The Jenny Graves Prize for best student short presentation}{ComBio22, Melbourne, Australia}{2022}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{LTU Full Fee Research Scholarship (LTUFFRS) Award}{Melbourne, Australia}{2019-2023}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{LTU Postgraduate Research Scholarship (LTUPRS) Award}{Melbourne, Australia}{2019-2023}{}\vspace{-4.0mm}
    \cventry{Australian Society of Parasitology}{Australian Society of Parasitologists (ASP) student travel grant}{Adelaide, Australia}{2019}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{Pro Vice Chancellor's Commendation 2018}{Melbourne, Australia}{2019}{}\vspace{-4.0mm}
    \cventry{Master's poster session (La Trobe University)}{Research Poster Excellence Award}{Melbourne, Australia}{2019}{}\vspace{-4.0mm}
    \cventry{La Trobe University}{La Trobe College Excellence Scholarship}{Melbourne, Australia}{2017-2019}{}\vspace{-4.0mm}
    \cventry{Kathmandu University}{Merit based Scholarship}{Dhulikhel, Nepal}{2013-2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{research-grants}{%
\section{Research grants}\label{research-grants}}

\begin{cventries}
    \cventry{UNICEF/UNDP/World Bank/WHO Special Programme for Research and Training in Tropical Diseases (TDR/WHO) (US\$108,000)}{Co-investigator/Sub-awardee}{}{2021-2022}{\begin{cvitems}
\item Population genetic tools for onchocerciasis control programmes to determine transmission zones.
\end{cvitems}}
\end{cventries}
\pagebreak

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{cventries}
    \cventry{\textbf{Journal publications}}{}{}{}{\begin{cvitems}
\item \textbf{Shrestha H}, McCulloch K, Hedtke SM, Grant WN. Geospatial modeling of pre-intervention nodule prevalence of \textit{Onchocerca volvulus} in Ethiopia as an aid to onchocerciasis elimination. Cotton J, editor. PLoS Negl Trop Dis. 2022 Jul 18;16(7):e0010620.
\item Gyawali P, Tamrakar D, Shrestha A, \textbf{Shrestha H}, Karmacharya S, Bhattarai S, et al. Consumer acceptance and preference for brown rice-A mixed-method qualitative study from Nepal. Food Sci Nutr. 2022 Mar 4;fsn3.2803.
\item Gyawali P, \textbf{Shrestha H}, Pant V, Risal P, Gautam S. C-reactive Protein to Albumin Ratio among Patients Admitted to Intensive Care Unit of a Tertiary Care Hospital: A Descriptive Crosssectional Study. J Nepal Med Assoc. 2021 Dec 11;59(244):1247-51.
\item R Shrestha, DP Subedi, S Adhikari, A Maharjan, \textbf{H Shrestha}, GR Pandey (2017). Experimental Study of Atmospheric Pressure Argon Plasma Jet-Induced Strand Breakage in Large DNA Molecules, Plasma Medicine, vol. 7, no. 1. doi:10.1615/PlasmaMed.2017019986
\item J Shrestha Manandhar, R Shrestha, N Basnet, P Silwal, \textbf{H Shrestha}, A Risal, D Kunwar (2017). Study of Adherence Pattern of Antidepressants in Patients with Depression, Kathmandu University Medical Journal (KUMJ), vol. 15, no. 57, pp: 3-9. PMID: 29446354
\item JTM Shrestha, \textbf{H Shrestha}, M Prajapati, A Karkee, A Maharjan (2017). Adverse Effcts of Oral Hypoglycemic Agents and Adherence to them among Patients with Type 2 Diabetes Mellitus in Nepal, Journal of Lumbini Medical College, vol. 5, no. 1, pp. 34-40. doi:10.22502/jlmc.v5i1.126
\end{cvitems}}
    \cventry{\textbf{Preprint}}{}{}{}{\begin{cvitems}
\item \textbf{Shrestha H}, McCulloch K, Chisholm RH, Armoo S, Vierigh F, Sirwani N, et al. Synthesising environmental, epidemiological, and genetic data to assist decision making for onchocerciasis elimination. Epidemiology; 2023 Feb. doi:10.1101/2023.02.14.23285937
\end{cvitems}}
    \cventry{\textbf{Conference presentations and posters}}{}{}{}{\begin{cvitems}
\item \textbf{H Shrestha}, K McCulloch, SM Hedtke, WN Grant (2021). Geospatial modeling of the baseline \textit{Onchocerca volvulus} nodule prevalence in Ethiopia as an aid to elimination. Poster presentation at ASTMH 2022 Annual Meeting,  Seattle Convention Center, United States, 30 Oct - 3 Nov, 2022.
\item \textbf{H Shrestha}, SM Hedtke, RH Chisholm, WN Grant (2021). Landscape genetics and persistence of Onchocerciasis transmission in Ghana. Lightning talk at ComBio22, Melbourne Convention and Exhibition Centre (MCEC),27-30 Sep, 2022.
\item \textbf{H Shrestha}, K McCulloch, SM Hedtke, WN Grant (2021). Landscape genetics to determine factors for ongoing transmission of onchocerciasis in the transition region of Ghana. Science bite talk at PAM HDR Research Symposium 2021 held online on December 15, 2021.
\item \textbf{H Shrestha}, SM Hedtke, K McCulloch, WN Grant (2021). Landscape genetics to determine factors for ongoing transmission of onchocerciasis in the transition region of Ghana. Oral presentation (15 mins) at COMBINE Student Symposium (Virtual), Nov 22, 2021.
\item \textbf{H Shrestha}, K McCulloch, SM Hedtke, SM Feleke, WN Grant (2021). Geospatial analysis of pre-intervention prevalence of onchocerciasis in Ethiopia. Australian Society of Parasitology Online Conference (Virtual). Jun 23-25, 2021.
\item \textbf{H Shrestha}, K McCulloch, SM Hedtke, WN Grant (2021). Geospatial mapping of onchocerciasis prevalence in Ethiopia. Spatial and Temporal Statistics Symposium (STSS), University of Wollongong (Virtual), February 17-19, 2021.
\item \textbf{H Shrestha}, SM Hedtke, K McCulloch, WN Grant (2020). Identifying spatial patterns of onchocerciasis transmission using landscape analysis. Science bite talk at PAM Research Symposium 2020 held online on December 10 and 11, 2020.
\item WN Grant, SM Hedtke, K McCulloch, S Wanji, \textbf{H Shrestha} (2020). Elucidating ivermectin's action on reproduction of adult female \textit{Onchocerca volvulus} from embryogram data: the basis for the embryostatic phenotype and sub-optimal response. Anthelmintics: Discovery to Resistance IV, Los Angeles, California, February 3-7, 2020
\item \textbf{H Shrestha} (2019). Elucidating ivermectin's action on reproduction of adult female \textit{Onchocerca volvulus} from embryogram data: the basis for the embryostatic phenotype. PRISM2 Annual Conference, Woodward Conference Centre, Carlton, Victoria, November 12-13, 2019.
\item W Grant, S Hedtke, S Wanji, \textbf{H Shrestha} (2019). Ivermectin and fertility in nematodes. The second Australian \textit{C. elegans} Symposium (ACES, 2019), Queensland Brain Institue, The University of Queensland, Brisbane, Queensland, October 23-25, 2019.
\item \textbf{H Shrestha}, SM Hedtke, K McCulloch, S Wanji, WN Grant (2019). Effect of ivermectin treatment on adult female Onchocerca volvulus from embryogram data: evidence for periodicity of reproduction and the basis for the embryostatic phenotype. Oral presentation (15 mins) at annual meeting of Australian Society for Parasitology, Adelaide Convention Centre, South Australia, July 8-11, 2019.
\item S Gautam, P Gyawali, J Singh, \textbf{H Shrestha} (2016). Assessment of C-Reactive Protein/Albumin Ratio in Critically Ill Patients with Various Underlying Diseases. Poster presentation at Second Annual Scientific Meeting (NACC-CON 2016) at Dhulikhel Hospital Kathamandu University Hospital, Nepal, August 20-21, 2016.
\item A Maharjan, \textbf{H Shrestha}, S Shrestha (2016). Prevalence of Rheumatic Symptoms in Urban Population of Kathmandu Valley. Poster presentation at 7th National Conference on Science and Technology, Kathmandu, Nepal, March 29-21, 2016.
\item \textbf{H Shrestha}, A Maharjan, S Shrestha (2016). Attitudes Towards Menstruation of Pre-menstruating Adolescent School Girls. Poster presentation at 7th National Conference on Science and Technology, Kathmandu, Nepal, March 29-21, 2016.
\end{cvitems}}
\end{cventries}

\hypertarget{volunteering-experience}{%
\section{Volunteering experience}\label{volunteering-experience}}

\begin{cventries}
    \cventry{Co-founder and Lead}{}{}{}{\begin{cvitems}
\item Aug, 2022-Ongoing: \href{http://ankaanalytica.com/}{Anka Analytica}
\end{cvitems}}
    \cventry{Treasurer}{}{}{}{\begin{cvitems}
\item Jan, 2022-Dec, 2022: Australian Computational Biology and Bioinformatics Student Society (COMBINE-AU)
\end{cvitems}}
    \cventry{Executive committee member}{}{}{}{\begin{cvitems}
\item Jan, 2020- Dec, 2021: Australian Computational Biology and Bioinformatics Student Society (COMBINE-AU)
\item Jan-Dec, 2020: Physiology, Anatomy and Microbiology-High Degree Research (PAM-HDR) Student Society
\item 2013-2014: Kathmandu University Youth Red Cross Circle (KUYRCC)
\end{cvitems}}
    \cventry{Instructor}{}{}{}{\begin{cvitems}
\item 13 and 15 Apr, 2021: Introduction to R and Data Visualisation Workshop, COMBINE-AU
\item 1-2 Sep, 2022,4 and 5 May, 2021: Introduction to Python, COMBINE-AU
\item 15-16 Sep, 2021: A day in the life of a bioinformatician, COMBINE-AU
\end{cvitems}}
    \cventry{Volunteer}{}{}{}{\begin{cvitems}
\item Feb, 2018:International Student Host at International Student Services, La Trobe University
\item Sep, 2017:Fund raising event by Olivia Newton - John Cancer Research Centre
\item Nov, 2016: Fifth Conference of South Asian Association of Physiologists
\item Apr, 2014: Program Coordinator in One Day Health Camp (Red Cross Circle)
\end{cvitems}}
\end{cventries}

\hypertarget{trainings-and-workshops-attended}{%
\section{Trainings and workshops
attended}\label{trainings-and-workshops-attended}}

\begin{cventries}
    \cventry{\textbf{Programming and modelling workshops}}{}{}{}{\begin{cvitems}
\item Dec 1 2022: Symposium on Bioinformatics Entrepreneurship and Industry (SBEI2022), ABACBS, RMIT University, Melbourne
\item Dec 2, 2022: Oracle - Using Oracle Cloud for Bioinformatics, Oracle for Research, ABACBS, Melbourne
\item Aug 17-18, 2022: HPC201: Getting started with HPC using PBS Pro (Virtual), Intersect
\item Apr 4 2022: 1-Day Introduction to AMD GPUs (AMD Instinct Architecture and ROCm) (Virtual), Pawsey Supercomputing Centre
\item Oct 27-28, 2021: \href{http://slchen-lab-training.s3-website-ap-southeast-1.amazonaws.com/}{AWS GIS workshop for online cloud genomics} (Virtual), Genome Institute of Singapore and Amazon Web Services
\item Jun 28, Jul 09, 2021: Data-Driven Modelling in Mathematical Biology (Virtual), MATRIX and AMSI
\item Jun 28 - Jul 02, 2021: Helminth Bioinformatics - Asia (Virtual), Welcome Connecting Science
\item Nov 02-06, 2020: Hierarchical Modelling of Species Communities with the R-package Hmsc (virtual), University of Helsinki, Finland
\item Sep 16, 2019: COMBINE R package development workshop, COMBINE-AU, Walter and Eliza Hall Institute, Melbourne, Australia
\item Aug 08 - Sep 12, 2019: 6-Week Technical Deep Learning Workshop, Braneshop, Bluerock, Melbourne, Australia
\item Feb 04-08, 2019: Mplus course on Structural Equation Modelling (SEM) and Multilevel Modelling (MLM), University of Melbourne, Melbourne, Australia
\item Dec 14, 2018: G*Power Workshop, La Trobe University, Melbourne, Australia
\item Feb 25, 2017: Data analysis using Python, IT Training-Nepal, Kathmandu, Nepal
\end{cvitems}}
    \cventry{\textbf{Conferences}}{}{}{}{\begin{cvitems}
\item Jun 07-09, 2021: Genomic Epidemiology of Malaria (Virtual), Welcome Connecting Science
\item Jul 22-26, 2020: ISEC2020 International Statistical Ecology Conference (Virtual), Statistics in Ecology, Environment and Conservation, Sydney, Australia
\item Jun 8-12 2020: Advancing knowledge about spatial modelling, infectious diseases, environment and health (Virtual), Fields Institute for Research in Mathematical Sciences, Toronto, Canada
\item Mar 13-15, 2017: Regional workshop on Zoonotic Diseases Pandemic Preparedness for South Asia Using One Health Platform, Centre for Molecular Dynamics-Nepal, Kathmandu, Nepal
\end{cvitems}}
    \cventry{\textbf{Mentorship}}{}{}{}{\begin{cvitems}
\item Sep 2022-Ongoing: IMNIS industry mentorship by Dr. Julia Hill (Head of Commercialisation at Children's Medical Research Institute)       
\end{cvitems}}   
    \cventry{\textbf{Summer school}}{}{}{}{\begin{cvitems}
\item Jan 06-31, 2020: Dynamic processes spreading on Networks, La Trobe University, Australia
\item Jan 06-31, 2020: Random Fields: Mathematical theory and application in spatial statistics, La Trobe University, Australia
\end{cvitems}}
    \cventry{\textbf{Miscellaneous workshops}}{}{}{}{\begin{cvitems}
\item Aug 01, 2017: Working with recombinant DNA, La Trobe University, Melbourne, Australia
\item Mar 21, 2016: One Day Seminar on Intellectual Property Rights, Kathmandu University, Dhulikhel, Nepal
\end{cvitems}}
\end{cventries}

\hypertarget{References}{%
\section{References}\label{References}}

\newcommand*{\emaillink}[1]{{\fontsize{8pt}{1em}\bodyfont\scshape\color{awesome} #1}}

\newcommand{\cvdoublecolumn}[2]{%
	\begin{minipage}[t]{{.45\linewidth}}#1\end{minipage}%
	\hfill%
	\begin{minipage}[t]{{.45\linewidth}}#2\end{minipage}%
}

\newcommand{\cvreference}[6]{
	\entrytitlestyle{#1}\newline
	\descriptionstyle{#2}\newline
	\descriptionstyle{#3}\newline
	\faHome\acvHeaderIconSep~\descriptionstyle{#4}\newline
	\faMobile\acvHeaderIconSep~\descriptionstyle{#5}\newline
	\href{mailto:#6}{\faEnvelope\acvHeaderIconSep~\emaillink{#6}\newline}}

\cvdoublecolumn{\cvreference{Prof Warwick Grant}
	{Head of Discipline, Genetics}
	{Department of Environment and Genetics, La Trobe University}
	{Bundoora, Victoria, Australia}
	{+61 400 502 072}
	{W.Grant@latrobe.edu.au}
}
{\cvreference{Dr Shannon Hedtke}
	{Research Fellow}
	{Department of Environment and Genetics, La Trobe University}
	{Bundoora, Victoria, Australia}
	{+61 449 207 900}
	{S.Hedtke@latrobe.edu.au}
}

\end{document}
